### 2015-12-28 Projects/Exploratory_Convective_PPE/Report/convective_ppe_heating.tex
edits to ppe report

\chapter*{\centering Abstract}
\pagenumbering{gobble}
The overall objective of this interagency agreement between the United States Fire Administration (USFA) and the National Institute of Standards and Technology (NIST) is to better define the thermal limits of the operational fire environment, its impact on structural firefighting personal protective equipment (PPE), and deliver this information to the appropriate standards groups and the fire service. Without an accurate understanding of the conditions of environments in which a firefighter can safely operate, firefighters are more at risk of injuries and death.

@@

\chapter{Existing Tests}
Existing Tests - high thermal flux, short exposure

\section{Thermal Protective Performance}
TTP Test - PPE

\section{ThemoMan}
Thermo man - (pyro man) PPE

@@

While under bench scale test conditions it is less difficult to decouple convective heating from a radiant heat exposure.  However with current test apparatus while convective heating is dominant, there is some level of radiant heating that is contributing to the heat transfer.
Under full scale conditions in a flow path the PPE is exposed to a combination of convective and radiative heating.
LoDDs
Use - Cherry Road and San Francisco as examples
Items examined

Turnout gear material
Helmets    thermoplastic shell, fiberglas shell and leather shell
Facepieces
Old Scott AV 3000?,  New Scott 3000HT
MSA Old  and New MSA 7
Tests
Heat Gun Exposure?
Flow loops
	Plunge test
		Temperature, velocity, heat flux measure?
	Thermal Flow Loop
		Temperature, velocity, heat flux
Full Scale
	Delco Exposures

>>>>

\chapter*{\centering Abstract}
\pagenumbering{gobble}
The overall objective of this inter-agency agreement between the United States Fire Administration (USFA) and the National Institute of Standards and Technology (NIST) is to better define the thermal limits of the operational fire environment, its impact on structural firefighting personal protective equipment (PPE), and deliver this information to the appropriate standards groups and the fire service. Without an accurate understanding of the conditions of environments in which a firefighter can safely operate, firefighters are more at risk of injuries and death.

@@

{\bf LoDDs - Cherry Road and San Francisco as examples}

\chapter{Existing Tests}

Existing Tests - high thermal flux, short exposure

\section{Thermal Protective Performance}
TPP Test - PPE

\section{ThermoMan}
Thermo man - (pyro man) PPE

@@

While under bench scale test conditions it is less difficult to decouple convective heating from a radiant heat exposure.  However with current test apparatus while convective heating is dominant, there is some level of radiant heating that is contributing to the heat transfer.
Under full scale conditions in a flow path the PPE is exposed to a combination of convective and radiative heating.

\chapter{New Tests Investigated}
Turnout gear material
Helmets    thermoplastic shell, fiberglass shell and leather shell

items examined:\\
Facepieces
Old Scott AV 3000?,  New Scott 3000HT
MSA Old  and New MSA 7\\

\section{Heat Gun Exposure}

\section{Flow Loops}

\subsection{Plunge test}
		Temperature, velocity, heat flux measure?

\begin{figure}[ht!]
\includegraphics[width=\columnwidth]{../../../Projects/Gear_Plunge_Tests/Pictures/Plunge_2}
\caption{Image of plunge test apparatus configured to test a turnout gear sample.}
\label{fig:plunge_pic}
\end{figure}

\subsection{Thermal Flow Loop}
		Temperature, velocity, heat flux

\section{Full Scale Tests}
	Delco Exposures
